Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-15 analysis/paper/paper.Rmd
Update conclusions in paper
Fix misspelled "Philippines"

The AWD technology has been identified as promising climate smart practice for different rice growing regions that can stabilize rice production in water scarce areas as well as help reduce the carbon footprint of rice production. Various countries, *e.g.*, Bangladesh, Vietnam, Thailand and the Philip pines, plan to widely apply AWD to local rice production [@MOEF2015]. However, a change in water regime in rice fields on large scale might encompass different other effects, for example related to plant health.

@@

In 2015 both the N~1~ and N~2~ treatments were significantly different than the control N~0~ treatment. The AWD water management was also significantly different from the control flooding treatment.

@@

In 2015 both the N~1~ and N~2~ treatments were significantly different than the N~0~ treatment. The AWD water management was also significantly different from the control flooding treatment.

>>>>

The AWD technology has been identified as promising climate smart practice for different rice growing regions that can stabilize rice production in water scarce areas as well as help reduce the carbon footprint of rice production. Various countries, *e.g.*, Bangladesh, Vietnam, Thailand and the Philippines, plan to widely apply AWD to local rice production [@MOEF2015]. However, a change in water regime in rice fields on large scale might encompass different other effects, for example related to plant health.

@@

In 2015 both the N~1~ and N~2~ treatments were significantly different than the control N~0~ treatment. However, the AWD water management was not significantly different from the FLD treatment.

@@

In 2015 both the N~1~ and N~2~ treatments were significantly different than the N~0~ treatment. However, the AWD water management was not significantly different from the FLD treatment.
